Differences in Homicide Case Information Indicates Why Justice is Not Served

### 2024-12-04 paper/paper.qmd
Finished abstract

---
title: "Differences in Homicide Case Information Indicates Why Justice is Not Served"
subtitle: "An analysis of solved and unsolved homicides from 2010 to 2017 in one of the United States's 2 largest cities, Chicago and Los Angeles"
author: 
  - Emily Su
thanks: "Code and data are available at: [https://github.com/moonsdust/unsolved-murders](https://github.com/moonsdust/unsolved-murders)."
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format:
  pdf:
    toc: true
number-sections: true
bibliography: references.bib
---

@@

For the remainder of the paper, the data section [@sec-data] goes over the data we used and its features and limitations, how the dataset was obtained, our variables of interest for our model and preliminary analysis, and a bit of our data cleaning process. In the model section [@sec-model], it discusses the type of model we used, the relationships between variables in our model, and the justification for our model. The results section [@sec-results] contains tables and graphs created based on our data and the results from our model. In the discussion section [@sec-discussion], it goes over what we did in our results, explaining the meaning of our findings, the implications of our findings to the real world, and areas of improvement and suggestions for future works.

>>>>

---
title: "Differences in Homicide Case Information Indicates Why Justice is Not Served"
subtitle: "An analysis of solved and unsolved homicides from 2010 to 2017 in one of the United States's 2 largest cities, Chicago and Los Angeles"
author: 
  - Emily Su
thanks: "Code and data are available at: [https://github.com/moonsdust/unsolved-murders](https://github.com/moonsdust/unsolved-murders)."
date: today
date-format: long
abstract: "Despite Chicago Mayor Brandon Johnson announcing in 2024 that the Chicago Police Department had the highest homicide clearance rate of 54% in years, homicide clearance rates across the United States (US) have been decreasing since 1980, with more homicides going unsolved. This paper looks at patterns of homicide case information with the case resolution from 2010 to 2017 in two of the largest cities in the United States, Chicago and Los Angeles. We found that unsolved homicides are more likely to occur in Chicago compared to Los Angeles, and the majority of unsolved homicide victims are Black or Hispanic and are male. These findings can inform the public and US police departments of populations more vulnerable to having unsolved cases however further investigation is needed on the investigators involved in each unsolved homicide case."
format:
  pdf:
    toc: true
number-sections: true
bibliography: references.bib
---

@@

For the remainder of the paper, the data section [@sec-data] goes over the data we used and its features and limitations, how the dataset was obtained, our variables of interest for our model and preliminary analysis, and a bit of our data cleaning process. In the model section [@sec-model], it discusses the type of model we used, the relationships between variables in our model, and the justification for our model. The results section [@sec-results] contains tables and graphs created based on our data and the results from our model. In the discussion section [@sec-discussion], it goes over what we did in our results, explaining the meaning of our findings, the implications of our findings to the real world, and areas of improvement and suggestions for future works. In the appendix [@sec-appendix], it includes a link to the dashboard that includes interactive versions of the graphs in this paper, additional tables, notes on reproducing and code styling, model diagnostics and validation, and our idealized survey and methodology to gather more data on investigators responsible for homicide cases.
